---
title: "Naive Bayes"
author: "Jameson Watts, Ph.D."
date: "02/01/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_smooth: true
    number_sections: true
    df_print: kable
    fig_width: 11
---
<style>
strong{
  color: #018080;
}
table.rmdtable th {
    background: #791716;
}

</style>

## Agenda

1. The Naive Bayes algorithm
2. Tidy text and bag of words
3. The new tidymodels package

# The Naive Bayes Algorithm

## Algorithm

$ p(C|x) = \frac{p(C \space\&\space x)}{p(x)}$

## Setup

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(caret)
library(naivebayes)
library(fastDummies)
source('theme.R')

wine = as.data.frame(read_rds("../resources/pinot-project.rds")) 
```

## Some basic features

```{r}
wino <- wine %>% 
  mutate(year_f = as.factor(year)) %>% 
  mutate(cherry = str_detect(description,"cherry")) %>% 
  mutate(chocolate = str_detect(description,"chocolate")) %>%
  mutate(earth = str_detect(description,"earth")) %>%
  select(-description, year)

glimpse(wino)
```

## A couple conditional probabilities

$p(Oregon | cherry) = \frac{p(Oregon \space\&\space Cherry)}{p(Cherry)}$

```{r}
oregon_and_cherry <- nrow(filter(wino, province=="Oregon" & cherry))/nrow(wino)
cherry <- nrow(filter(wino, cherry))/nrow(wino)
oregon_and_cherry/cherry
```

## How about New York?
$p(NY | cherry) = \frac{p(NY \space\&\space Cherry)}{p(Cherry)}$

```{r}
ny_and_cherry <- nrow(filter(wino, province=="New_York" & cherry))/nrow(wino)
ny_and_cherry/cherry
```


## A basic model

```{r}
set.seed(5004)
wine_index <- createDataPartition(wino$province, p = 0.80, list = FALSE)
train <- wino[ wine_index, ]
test <- wino[-wine_index, ]

grid <- expand.grid(usekernel = c(T, F), laplace = c(T,F), adjust = T)
grid

fit <- train(province ~ .,
             data = train, 
             method = "naive_bayes",
             tuneGrid = grid,
             metric = "Kappa",
             trControl = trainControl(method = "cv"))
fit
```

What's going on here?

## Maybe bin the data?

```{r}
wino <- wino %>%
  select(-starts_with("year_")) %>% 
  mutate(points_f = case_when(
    points < 90 ~ "low",
    points >= 90 & points < 96 ~ "med",
    points >= 96 ~ "high"
  )
           )  %>% 
  mutate(price_f = case_when(
    price < 16 ~ "low",
    price >= 16 & price < 41 ~ "med",
    price >= 41 ~ "high"
  )
           )  %>% 
  mutate(year_f = case_when(
    year < 2005 ~ "old",
    year >= 2005 & year < 2011 ~ "recent",
    year >= 2011 ~ "current"
  )
           ) %>% 
  select(-price,-points,-year)

  head(wino)
```

## Binned model

```{r}
train <- wino[ wine_index, ]
test <- wino[-wine_index, ]

fit <- train(province ~ .,
             data = train, 
             method = "naive_bayes",
             tuneGrid = grid,
             metric = "Kappa",
             trControl = trainControl(method = "cv"))
fit
```

Little better, but let's look at the confusion matrix to see what might be going on.

## Confusion Matrix
```{r}
confusionMatrix(predict(fit, test),factor(test$province))
```

##### Naive bayes is best when you want to consider a bunch of predictors simultaneously to get a 'holistic' view.


# Tidytext and frequency distributions

## Tidytext

```{r}
library(tidytext)
data(stop_words)

head(stop_words, 25)$word
```

## Create document term matrix

```{r}
wine <- rowid_to_column(wine, "ID") # so we can summarize and link back to original data set
df <- wine %>%
  unnest_tokens(word, description) %>%
  anti_join(stop_words) %>% # get rid of stop words
  filter(word != "wine") %>%
  filter(word != "pinot") %>%
  count(ID, word) %>% 
  group_by(ID) %>% 
  mutate(freq = n/sum(n)) %>% 
  mutate(exists = (n>0)) %>% 
  ungroup %>% 
  group_by(word) %>% 
  mutate(total = sum(n))

head(df, 10)
```

## Top words in database

```{r}
df %>% 
  count(word) %>%
  arrange(desc(n)) %>% 
  head(25)
```

## Pivot wide and rejoin with wine

```{r}
wino <- df %>% 
  filter(total > 1000) %>% 
  pivot_wider(id_cols = ID, names_from = word, values_from = exists, values_fill = list(exists=0)) %>% 
  right_join(select(wine,ID, province)) %>% 
  drop_na()

head(wino, 10) %>% 
  select(1:5,province)
```

## A new model

```{r}
set.seed(5004)
wine_index <- createDataPartition(wino$province, p = 0.80, list = FALSE)
train <- wino[ wine_index, ]
test <- wino[-wine_index, ]

fit <- train(province ~ .,
             data = train, 
             method = "naive_bayes",
             tuneGrid = expand.grid(usekernel = T, laplace = T, adjust = T),
             metric = "Kappa",
             trControl = trainControl(method = "cv"))
fit
```

...now things are getting better.

## Confusion Matrix
```{r}
confusionMatrix(predict(fit, test),factor(test$province))
```

## Maybe we can find words associated with our sparse provinces?

```{r}

df %>% 
  left_join(select(wine, ID, province), by = "ID") %>% 
  count(province, word) %>%
  group_by(province) %>% 
  top_n(10,n) %>% 
  arrange(province, desc(n))
```

## Group exercise

Use the top words by province to...

1. Engineer more features that capture the essence of Casablanca, Marlborough and New York
2. Use them to run naive bayes models that achieve Kappa > 0.4

# Intro to Tidymodels

## Splitting the data

```{r}
library(tidymodels)
library(discrim)
wine = as.data.frame(read_rds("../resources/pinot-project.rds")) %>% 
  select(-description)
wine_split <- initial_split(wine)
train <- training(wine_split)
test <- testing(wine_split)
```

## Model specification

```{r}
lm_spec <- linear_reg() %>%
  set_engine(engine = "lm")

lm_spec
```

## Fit the Model

```{r}
lm_fit <- lm_spec %>%
  fit(price ~ .,
    data = train
  )

lm_fit
```

## Some references

https://rviews.rstudio.com/2019/06/19/a-gentle-intro-to-tidymodels/

https://juliasilge.com/blog/intro-tidymodels/
