---
title: "Neural Networks"
author: "Jameson Watts, Ph.D."
date: "04/04/2020"
output: 
  html_document:
    df_print: kable
    fig_width: 11
    fig_height: 8
---

## Agenda

1. Review of last week and modeling assignment 2
2. Overview of neural networks
3. Basic regression and classification with tensor flow

## Set up tensorflow

In the console

> install_tensorflow(version = "1.15")

*Note:* You may want to make sure you have the latest reticulate version installed.

## Setup
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(reticulate)
library(tensorflow)
library(tfestimators)
```

## Check tensorflow setup
```{r}
tf_config()
```

## Create a simple dataset
```{r}
wine <- read_rds("../resources/pinot-project.rds") %>% 
  select(price, province, points) %>% 
  rownames_to_column("id") %>% 
  mutate(exists=T) %>% 
  pivot_wider(names_from = province, values_from = exists, values_fill = c(exists=F)) %>% 
  mutate(price=log(price)) %>% 
  select(-id) %>% 
  mutate_if(is_numeric,scale) %>% 
  mutate_if(is_logical,as.integer)

## create training and test partitions
train_rows <- sample(1:nrow(wine), size = 0.8 * nrow(wine))
train <- wine[train_rows,] 
test <-wine[-train_rows,]

head(train)
```


## Create necessary inputs for train function
```{r}
ftr_colns <- feature_columns( 
  tf$feature_column$numeric_column("points"),
  tf$feature_column$categorical_column_with_identity("Oregon",2),
  tf$feature_column$categorical_column_with_identity("California",2),
  tf$feature_column$categorical_column_with_identity("Burgundy",2)
)

wodel <- linear_regressor(feature_columns=ftr_colns)

winput = function(data){ 
  input_fn(data, features = c("points","Oregon","California","Burgundy"), response = "price")
}

```

## Train the model

```{r}
## Assigns model to wodel
wrain <- train(wodel,winput(train))
wrain
## Evaluates out of sample using wodel
weval <- evaluate(wodel,winput(test))
weval

# pr <- predict(wodel,winput(test))
# rbind_all(pr$predictions)
# pr$predictions[][1]
```

## Build a basic classification model

```{r}
wine <- read_rds("../resources/pinot-project.rds") %>% 
  select(province, price, points) %>%
  mutate(price=log(price)) %>% 
  mutate_if(is_numeric,scale) 


## create training and test partitions
train_rows <- sample(1:nrow(wine), size = 0.8 * nrow(wine))
train <- wine[train_rows,] 
test <-wine[-train_rows,]

head(train)
```

## Create necessary inputs for train function
```{r}
ftr_colns <- feature_columns( 
  tf$feature_column$numeric_column("price"),
  tf$feature_column$numeric_column("points")
)

wodel <- linear_classifier(feature_columns=ftr_colns,
                           label_vocabulary = c("Oregon","California","Burgundy","Marlborough","Casablanca_Valley","New_York"),
                           n_classes = 6)

winput = function(data){ 
  input_fn(data, features = c("price","points"), response = "province")
}

```

## Train the model

```{r}
## Assigns model to wodel
wrain <- train(wodel,winput(train))
wrain
## Evaluates out of sample using wodel
weval <- evaluate(wodel,winput(test))
weval

pr <- predict(wodel,winput(test))
```

## How about a deep neural net?

```{r}
wodel <-
    dnn_classifier(
      feature_columns = ftr_colns,
      hidden_units = c(3, 3),
      label_vocabulary = c("Oregon","California","Burgundy","Marlborough","Casablanca_Valley","New_York"),
      n_classes = 6,
      optimizer = "Adagrad",
      model_dir = "../models"
    )

## Assigns model to wodel
wrain <- train(wodel,winput(train))
wrain
## Evaluates out of sample using wodel
weval <- evaluate(wodel,winput(test))
weval

tensorboard(log_dir = "../models")
```


# References

https://tensorflow.rstudio.com/


