---
title: "Homework 3"
author: ""
date: "02/08/2021"
output: 
  html_document:
    df_print: kable
    fig_width: 11
    fig_height: 8
---

**Directions:**

Please turn in **both** a knitted HTML file *and* your Rmd file on WISE.

Good luck!

# 1. Setup (1pt)

Change the author of this RMD file to be yourself and modify the below code so that you can successfully load the 'wine.rds' data file from your own computer.

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(caret)
wine = read_rds("../resources/pinot.rds")
```

## 2. KNN Concepts (5pts)

Explain how the choice of K affects the quality of your prediction when using a K Nearest Neighbors algorithm.

**Answer:** (write your answer here)

## 3. Feature Engineering (3pts)

1. Remove the taster_name column from the data
2. Create a version of the year column that is a factor (instead of numeric)
3. Create dummy variables that indicate the presence of "cherry", "chocolate" and "earth" in the description
4. Create 3 new features that represent the interaction between time and the cherry, chocolate and earth inidicators
5. Remove the description column from the data

```{r}

```
## 4. Preprocessing (3pts)

1. Preprocess the dataframe that you created in the previous question using BoxCox, centering and scaling of the numeric features
2. Create dummy variables for the year factor column

```{r}

```


## 5. Running KNN (5pts)

1. Split your data into an 80/20 training and test set
2. Use Caret to run a KNN model that uses your engineered features to predict province
  - use 5-fold cross validated subsampling 
  - allow Caret to try 15 different values for K
3. Display the confusion matrix on the test data


```{r}

```

## 6. Kappa (2pts)

Is this a good value of Kappa? Why or why not?

**Answer:** (write your answer here)

## 7. Improvement (2pts)

Looking at the confusion matrix, where do you see room for improvement in your predictions?

**Answer:** (write your answer here)
