---
title: "Homework 4"
author: ""
date: "02/15/2021"
output: 
  html_document:
    df_print: kable
    fig_width: 11
    fig_height: 8
---

**Directions:**

Please turn in **both** a knitted HTML file *and* your Rmd file on WISE.

Good luck!

# 1. Setup (1pt)

Change the author of this RMD file to be yourself and modify the below code so that you can successfully load the 'wine.rds' data file from your own computer.

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(caret)
library(naivebayes)
wine = read_rds("../resources/pinot.rds")
```

# 2. Conditional Probability (3pts)

Calculate $P(Burgundy | Fruit)$

...i.e. the probability that a Pinot comes from Burgundy given it has the word 'fruit' in the description.

```{r}

```

# 3. Naive Bayes Algorithm (4pts)

1. Train a naive bayes algorithm to classify a wine's province,
2. using 80% of your data,
3. three features engineered from the description
4. and 5-fold cross validation.
5. Report Kappa after using your model to predict provinces in the holdout sample.

```{r}

```


# 4. Frequency differences (2pts)

List the three words that most distinguish New York Pinots from all other Pinots.

```{r}

```

# 5. Bonus (1pt)

Calculate the variance of the logged word-frequency distributions for each province.
